Efficient toolkit implementing best practices for principal component analysis of population genetic data

### 2019-11-13 paper-bedpca.tex
first version finished

@@

All code used for the analyses of this paper is available at \url{https://github.com/privefl/paper4-bedpca/tree/master/code}.

Package bigsnpr can be installed from GitHub (see \url{https://github.com/privefl/bigsnpr}).

A tutorial on the steps to perform PCA on 1000G data is available at \url{} [TODO].

>>>>

\vspace*{5em}

@@

All code used for this paper is available at \url{https://github.com/privefl/paper4-bedpca/tree/master/code}.
Package bigsnpr can be installed from GitHub (see \url{https://github.com/privefl/bigsnpr}).
A tutorial on the steps to perform PCA on 1000G data is available at \url{https://privefl.github.io/bigsnpr/articles/bedpca.html}.
